---
title: "R code for: Barbosa et al. Health-Environment-Economy Interactions Shaping Disease Landscapes: Exploring Disease Co-occurrence in the Brazilian Amazon"

author: "Milton Barbosa"
date: '2025-01-26'

output:
  html_document: default
  pdf_document: default
---
 
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=4, fig.height=4, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```


## GLLVM (Generalized linear latent variable models). See Niku et al. 2019, https://doi.org/10.1111/2041-210X.13303)
```{r include=FALSE}
rm(list=ls())
library(mvabund)
library(TMB)
library(gllvm)
library(tidyverse)
library(corrplot)
library(gclus)

# Read the matrix containing the disease cases (columns) by municipality
y<-as.matrix(read.csv("matrix_epidemio_state_2017.csv", header=TRUE, row.names=1, check.names=FALSE, na.strings = "omit"))

# Renaming the columns
colnames(y) <- c(
  "Chagas rural",
  "Chagas urban",
  "Malaria rural",
  "Malaria urban",
  "ATL rural",
  "ATL urban",
  "VL rural",
  "VL urban",
  "Dengue"
)

# Read the matrix containing the covariates (columns) by municipality
X<-read.csv("matrix_environ_tt_2017.csv", header=TRUE,check.names=FALSE, na.strings = "omit")

# Read the matrix containing the population (columns) by municipality
z<-as.matrix(read.csv("matrix_pop_2017.csv", header=TRUE, row.names=1, check.names=FALSE, na.strings = "omit"))

```

# Check the correlation among covariates
```{r echo=TRUE}
# Calculate the Spearman correlation matrix for the first 25 columns of X
cor.matrix <- cor(X[, 1:25], method = "spearman")

# Round the correlation values to 3 decimal places
cor_1 <- round(cor.matrix, 3)

# Replace correlations below 0.7 with NA for easier filtering
cor_1 <- ifelse(cor_1 < 0.7, NA, cor_1)

# Display the filtered correlation matrix
print(cor_1)

# Optionally, write the filtered correlation matrix to a CSV file
# write.csv(cor_1, "correl_variaveis.csv")

```

# Variable transformation
```{r echo=TRUE}
# Transform and scale selected variables in data frame X
X <- X %>% mutate(
    defor =    as.numeric(scale(log(X$defor+0.001))),
    dgfor =    as.numeric(scale(log(X$deorg+0.0001))),
    mining =   as.numeric(scale(log(X$mining+0.000001))),
    fire =     as.numeric(scale(log(X$fire+0.01))),
    core =     as.numeric(scale(log(X$core+0.1))),
    edge =     as.numeric(scale(sqrt(X$edge+(3/8)))),
    secveg =   as.numeric(scale(log(X$secveg+0.01))),
    pasture =  as.numeric(scale(sqrt(X$pasture+(3/8)))),
    crop =     as.numeric(scale(log(X$crop+0.01))),
    urban =    as.numeric(scale(log(X$urban+0.0001))),
    road =     as.numeric(scale(log(X$road+0.1))),
    port =     as.numeric(scale(log(X$port+0.1))),
    river =    as.numeric(scale(log(X$river+0.1))),
    precp =    as.numeric(scale(log(X$precp+0.001))),
    precn =    as.numeric(scale(log(X$precn+0.0001))),
    tempp =    as.numeric(scale(log(X$tempp+0.01))),
    ipm_rural= as.numeric(scale(log(X$ipm_rural+0.01))),
    ipm_urban= as.numeric(scale(log(X$ipm_urban+0.001))))

# Apply log transformation to the population matrix
z <- log(z)



# Set the plotting area to a 2x2 grid and adjust margins
par(mfrow = c(2, 2), mar = c(2, 2, 1, 1))

# Loop through the first 25 columns (or adjust for the number of columns) to create histograms
for (i in 1:25) {  # Adjust the range (1:4) based on how many plots you want to display at a time
  hist(X[, i], main = paste("Histogram of Column", i), xlab = "", col = "lightblue", border = "black")
}

# Plot the histogram for z
hist(z, main = "Histogram of z", xlab = "", col = "lightgreen", border = "black")
```


# Selecting the model structure (family, random effect, method) based on the AIC
```{r echo=TRUE, fig.height=9, fig.width=7}

# Fit models with different families and methods
fitp <- gllvm(y, family = "poisson")
fitp_2 <- gllvm(y, family = "poisson", row.eff = "random")
fitp_3 <- gllvm(y, family = "poisson", row.eff = "random", method = "LA")

fitnb <- gllvm(y, family = "negative.binomial")
fitnb_2 <- gllvm(y, family = "negative.binomial", row.eff = "random")
fitnb_3 <- gllvm(y, family = "negative.binomial", row.eff = "random", method = "LA") 

fitz <- gllvm(y, family = "ZIP", control.start = list(start.fit = fitp), method = "LA")
fitz_2 <- gllvm(y, family = "ZIP", row.eff = "random", control.start = list(start.fit = fitp_3), method = "LA")

# Compare models based on AIC
AIC(fitp, fitp_2, fitp_3, fitnb, fitnb_2, fitnb_3, fitz, fitz_2)

# Summarise the best model (assume fitnb_2 as an example here)
summary(fitnb_2)

# Inspect the selected model
par(mfrow = c(3, 2), mar = c(4, 4, 3, 2))
plot(fitnb_2, var.colors = 1)

```

# Fitting the null model with the seledcted structure
```{r}
fit_2<- gllvm(y, offset=z, family = "negative.binomial", method = "LA", num.lv = 2)

# Plot residuals
par(mfrow = c(3, 2), mar = c(4, 4, 3, 2))
plot(fit_2, mfrow = c(1,2))

```

# Ordinations of municipalities and diseases by number of cases - Null model
```{r echo=TRUE, fig.height=6, fig.width=6}

# Extract state information (assuming the state column is the 10th column)
states <- y[, 10] 

# Convert states to a factor with specified levels
states <- factor(states, levels = c("AC", "AM", "AP", "MA", "MT", "PA", "RO", "RR", "TO"))

# Assign symbols to each state
state_symbols <- match(states, unique(states))  # Assign unique symbols to each state
symbol_vector <- c(1, 2, 3, 4, 5, 6, 7, 8, 9)   # Define symbol set

# Define colours using the 'viridis' colour palette
colors_plasma <- viridis::viridis(length(unique(state_symbols)))  # Generate colours
symbol_colors <- colors_plasma[state_symbols]  # Assign colours based on states

# Set up the plotting area
par(mfrow = c(1, 1))

# Ordination plot
ordiplot(
  fitnb_2,                   # Fitted null model
  biplot = TRUE,             # Display biplot
  ind.spp = 9,               # Number of species (adjust as needed)
  alpha = 0.74,              # Transparency of points
  main = "Ordination of Municipalities",  # Title of the plot
  s.colors = symbol_colors,  # Colour palette for states
  symbols = TRUE,            # Use symbols for points
  pch = state_symbols,       # Symbols for states
  cex.spp = 1,               # Scaling for species points
  spp.colors = "blue"        # Colour for species points
) + 
abline(h = 0, v = 0, lty = 2)  # Add horizontal and vertical reference lines

# Add a legend to the plot
legend(
  "topleft",                 # Legend position
  legend = unique(states),   # Labels for states
  col = colors_plasma,       # Colours for legend items
  pch = symbol_vector,       # Symbols for legend items
  horiz = FALSE              # Vertical orientation
)
```

# Ordinations of municipalities coloured according to each covariate - Null model
```{r, echo=TRUE, fig.height=6, fig.width=6}

# Define an arbitrary colour palette (length 20)
rbPal <- c("#00FA9A", "#00EC9F", "#00DFA4", "#00D2A9", "#00C5AF", "#00B8B4", 
           "#00ABB9", "#009DBF", "#0090C4", "#0083C9", "#0076CF", "#0069D4", 
           "#005CD9", "#004EDF", "#0041E4", "#0034E9", "#0027EF", "#001AF4", 
           "#000DF9", "#0000FF")

# Set up a plotting area for 2x2 grid
par(mfrow = c(2, 2), mar = c(2, 2, 1, 1))

# Loop through the first 25 covariates in X
for (i in 1:ncol(X[, 1:25])) {
  # Assign colours to municipalities based on covariate values
  Col <- rbPal[as.numeric(cut(X[, i], breaks = 20))]
  
  # Ordination plot for each covariate
  ordiplot(
    fitnb_2,                  # Fitted null model
    symbols = TRUE,           # Use symbols for points
    s.colors = Col,           # Colour points based on covariate values
    main = colnames(X)[i],    # Title of the plot (name of the covariate)
    biplot = TRUE,            # Include biplot
    alpha = 0.8,              # Transparency for points
    cex.spp = 1,              # Size of species points
    spp.colors = "red"        # Colour for species points
  )
}
```

# Selecting the number of latent variables for the model with covariates
```{r, echo=TRUE, fig.height=4, fig.width=5}

# Set TT-2 as the reference level
X$ttclass <- factor(X$ttclass)
is.factor(X$ttclass)
X$ttclass <- relevel(X$ttclass, ref = "2")

# Model with 1 latent variable
fit_env_1_tt <- gllvm(y, X, formula = y ~ defor + dgfor + mining + fire + core + edge + secveg + pasture + crop + urban + road + port + river + precp + precn + tempp + ipm_rural + ipm_urban + ttclass, offset=z, family = "negative.binomial", row.eff = "random", num.lv = 1)

# Model with 2 latent variables
fit_env_2_tt <- gllvm(y, X, formula = y ~ defor + dgfor + mining + fire + core + edge + secveg + pasture + crop + urban + road + port + river + precp + precn + tempp + ipm_rural + ipm_urban + ttclass, offset=z, family = "negative.binomial", row.eff = "random", num.lv = 2)

# Model with 3 latent variables
fit_env_3_tt <- gllvm(y, X, formula = y ~ defor + dgfor + mining + fire + core + edge + secveg + pasture + crop + urban + road + port + river + precp + precn + tempp + ipm_rural + ipm_urban + ttclass, offset=z, family = "negative.binomial", row.eff = "random", num.lv = 3)

# Compare models based on AIC
AIC(fit_env_1_tt, fit_env_2_tt, fit_env_3_tt)

# Plot residuals
plot(fit_env_2_tt, mfrow = c(1,2))

```

# Model coefficients with all covariates and a standardised x-axis
```{r, echo=TRUE, fig.height=5, fig.width=5}
#coef(fit_env_1)
#confint(fit_env_1)

# Plotting model coefficients with confidence intervals
coefplot(
  fit_env_2_tt,                # Model object
  mfrow = c(2, 2),             # Arrange plots in a 2x2 grid
  order = FALSE,               # Do not reorder coefficients
  cex.ylab = 0.8,              # Scale the y-axis label text
  xlim.list = replicate(25, c(-3, 3), simplify = FALSE)  # Standardised x-axis for all plots
)

```
# Visualising the coefficients with a levelplot
```{r, echo=TRUE, fig.height=7, fig.width=7}
# Load the lattice library for levelplot
library(lattice)

# Extract coefficients from the fitted model
s <- coef(fit_env_2_tt)
ss <- s$Xcoef  # Extract the coefficients matrix

# Calculate the maximum absolute value of the coefficients for scaling
aa <- max(abs(ss))

# Define the colour palette (red to white to blue)
colort <- colorRampPalette(c("red", "white", "blue"))

# Generate the levelplot
levelplot(
  as.matrix(ss),                          # Convert coefficients to a matrix
  xlab = "Diseases",                      # Label for the x-axis
  ylab = "Socioenvironmental Variables",  # Label for the y-axis
  col.regions = colort(100),              # Colour gradient
  cex.lab = 1.3,                          # Size of axis labels
  at = seq(-aa, aa, length = 100),        # Colour scale limits
  scales = list(x = list(rot = 45))       # Rotate x-axis labels by 45 degrees
)

# Display a summary of the fitted model with correlation
summary(fit_env_2_tt, corr = TRUE)

```

# Residual correlation between diseases - model without (a) and with (b) covariates
```{r, echo=TRUE, fig.height=5, fig.width=10}

# Load necessary libraries
library(corrplot)
library(gclus)

# Residual correlation matrix for the model without covariates
cr0 <- getResidualCor(fit_2)

# Assign row and column names
colnames(cr0) <- c(
  "Chagas rural",
  "Chagas urban",
  "Malaria rural",
  "Malaria urban",
  "ATL rural",
  "ATL urban",
  "VL rural",
  "VL urban",
  "Dengue"
)
rownames(cr0) <- colnames(cr0)

# Residual correlation matrix for the model with covariates
cr <- getResidualCor(fit_env_2_tt)

# Assign row and column names
colnames(cr) <- c(
  "Chagas rural",
  "Chagas urban",
  "Malaria rural",
  "Malaria urban",
  "ATL rural",
  "ATL urban",
  "VL rural",
  "VL urban",
  "Dengue"
)
rownames(cr) <- colnames(cr)

# Set up the plotting area for side-by-side comparison
par(mfrow = c(1, 2))  # 1 row, 2 columns

# Plot the residual correlation matrix without covariates
corrplot(
  cr0[order.single(cr0), order.single(cr0)], 
  diag = FALSE, 
  type = "lower", 
  order = "alphabet", 
  addCoef.col = 'black', 
  method = "square", 
  tl.cex = 0.8, 
  tl.srt = 45, 
  tl.col = "red", 
  main = "(a) Model Without Covariates"
)

# Plot the residual correlation matrix with covariates
corrplot(
  cr[order.single(cr), order.single(cr)], 
  diag = FALSE, 
  type = "lower", 
  order = "alphabet", 
  addCoef.col = 'black', 
  method = "square", 
  tl.cex = 0.8, 
  tl.srt = 45, 
  tl.col = "red", 
  main = "(b) Model With Covariates"
)

# Optional: Save the residual correlation matrices to CSV
# write.csv(cr0, "correl_resid_sem_cov_2017.csv")
# write.csv(cr, "correl_resid_com_cov_2017.csv")

```


# Ordinations of municipalities and diseases by number of cases - model without (a) and with (b) covariates
```{r, echo=TRUE,fig.height=6, fig.width=11}

## Latent variables 1 and 2 – models without (a) and with (b) covariates
par(mfrow = c(1,2))
ordiplot(fit_2, biplot = TRUE, ind.spp = 9, alpha = 0.75, cex.spp = 1,
  spp.colors = "red", s.colors = 8, jitter = F, which.lvs = c(1, 2),
         main = "(a)")

ordiplot(fit_env_2_tt, biplot = TRUE, ind.spp = 9, alpha = 0.75, cex.spp = 1, 
         spp.colors = "red", s.colors = 8, jitter = F, which.lvs = c(1, 2),
         main = "(b)")

```

# Ordinations of municipalities and diseases by number of cases - model with covariates
```{r echo=TRUE, fig.height=6, fig.width=6}

# Extract state information (assuming the state column is the 10th column)
states <- y[, 10]

# Convert states to a factor with specified levels
states <- factor(states, levels = c("AC", "AM", "AP", "MA", "MT", "PA", "RO", "RR", "TO"))

# Match each unique state to a corresponding symbol
state_symbols <- match(states, unique(states))
symbol_vector <- c(1, 2, 3, 4, 5, 6, 7, 8, 9)  # Define symbols for states

# Define colors using the viridis palette
colors_plasma <- viridis::viridis(length(unique(state_symbols)))
symbol_colors <- colors_plasma[state_symbols]  # Assign colors based on state_symbols

# Set up the plotting area
par(mfrow = c(1, 1))

# Generate the ordination plot
ordiplot(
  fit_env_2_tt,              # Fitted model with covariates
  biplot = TRUE,             # Include a biplot
  ind.spp = 9,               # Number of species or components to display
  alpha = 0.74,              # Transparency for points
  main = "Ordination of Municipalities",  # Plot title
  s.colors = symbol_colors,  # Colors for state points
  symbols = TRUE,            # Use symbols for points
  pch = state_symbols,       # Point symbols based on states
  cex.spp = 1,               # Size of species points
  spp.colors = "blue"        # Color for species points
)

# Add horizontal and vertical reference lines
abline(h = 0, v = 0, lty = 2)

# Add a legend for the states
legend(
  "topleft",                # Position of the legend
  legend = unique(states),  # State names for the legend
  col = colors_plasma,      # Colors for the legend items
  pch = symbol_vector,      # Symbols for the legend items
  horiz = FALSE             # Vertical legend layout
)

```


# Ordinations of municipalities coloured according to each covariate - model with covariates
```{r eval=FALSE, fig.height=6, fig.width=6, include=FALSE}

# Define a colour palette
rbPal <- c("#00FA9A", "#00EC9F", "#00DFA4", "#00D2A9", "#00C5AF", "#00B8B4", 
           "#00ABB9", "#009DBF", "#0090C4", "#0083C9", "#0076CF", "#0069D4", 
           "#005CD9", "#004EDF", "#0041E4", "#0034E9", "#0027EF", "#001AF4", 
           "#000DF9", "#0000FF")

# Set up plotting area
par(mfrow = c(2, 2), mar = c(2, 2, 1, 1))

# Loop through each covariate in X
for (i in 1:ncol(X)) {
  # Assign colours based on covariate values
  Col <- rbPal[as.numeric(cut(X[, i], breaks = 20))]
  
  # Generate ordination plot
  ordiplot(
    fit_env_2,                   # Fitted model with covariates
    symbols = TRUE,              # Use symbols for points
    s.colors = Col,              # Colour points based on covariate values
    main = colnames(X)[i],       # Title of the plot (covariate name)
    biplot = TRUE,               # Include biplot
    alpha = 0.7,                 # Transparency for points
    cex.spp = 0.8,               # Size of species points
    which.lvs = c(1, 2),         # Latent variables to include in the plot
    spp.colors = "red"           # Colour for species points
  )
}

```

# Comparison of disease residual covariances between models with and without covariates and calculation of the proportion of residual covariance explained by the model with covariates.
```{r, echo=TRUE}
# Comparison of disease residual covariances between models with and without covariates

# Extract residual covariance matrices
rcov0 <- getResidualCov(fit_2, adjust = 0)             # Null model
rcov <- getResidualCov(fit_env_2_tt, adjust = 0)       # Model with covariates

# Display trace of the residual covariance matrices
rcov0$trace  # Total variance explained by the null model
rcov$trace   # Total variance explained by the model with covariates

# Calculate the proportion of residual covariance explained by the model with covariates
proportion_explained <- (1 - rcov$trace) / rcov0$trace
proportion_explained
```

# Extract model residuals per disease per municipality
```{r, echo=TRUE}

# Residuals for the null model
res0 <- residuals(fit_2, type = "response")
res0 <- as.data.frame(res0$residuals)

# Convert residuals to yearly incidence per 1000 inhabitants (null model)
resid_incidence_null <- as.matrix(((res0 / 5) / z) * 1000)

# Residuals for the model with covariates
res <- residuals(fit_env_2_tt, type = "response")
res <- as.data.frame(res$residuals)

# Convert residuals to yearly incidence per 1000 inhabitants (model with covariates)
resid_incidence <- as.matrix(((res / 5) / z) * 1000)

# Optional: Save residual incidence matrices to CSV
# write.csv(resid_incidence_null, "resid_model_null_2017_tt.csv", row.names = TRUE)
# write.csv(resid_incidence, "resid_model_with_covar_2017_tt.csv", row.names = TRUE)

```

# Calculate the observed and predicted incidence per years per 1000 inhabitants
```{r, echo=TRUE, fig.height=10, fig.width=10}
# Load necessary libraries
library(ggplot2)
library(patchwork)  # For combining plots

# Extract the linear predictor from the fitted model
pred <- as.data.frame(predict(fit_env_2_tt, type = "response"))

# Calculate observed incidence rates (cases per year per 1000 inhabitants). Divide the total cases over 5 years, then divide by the number of inhabitants of each municipality (matrix z), and multiply by 1000 to obtain the yearly incidence per 1000 inhabitants
obs_incid <- as.matrix(((y / 5) / z) * 1000) 

# write.csv(obs_incid, "incidencia_2017_year_1000_inhabit.csv", row.names = TRUE)

# Calculate predicted incidence rates (cases per year per 1000 inhabitants)
pred_incid <- as.matrix(((pred / 5) / z) * 1000)

# write.csv(pred_incid, "predito_2017_year_1000_inhabit_ss.csv", row.names = TRUE)

# Get the disease names from the column names of y
disease_names <- colnames(y)

# Initialize a list to store all the plots
plot_list <- list()

# Loop through all diseases and create plots
for (i in seq_along(disease_names)) {
  
  # Disease name
  disease <- disease_names[i]
  
  # Create a data frame for plotting
  plot_data <- data.frame(
    Municipality = 1:nrow(obs_incid),
    Observed = obs_incid[, i],
    Predicted = pred_incid[, i]
  )
  
  # Create the plot (remove individual x/y axis labels!)
  p <- ggplot(plot_data, aes(x = Observed, y = Predicted)) +
    geom_point(alpha = 0.5, color = "#2C3E50", size = 2) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", 
                color = "#E74C3C", size = 1) +
    labs(
      title = paste(disease),
      x = NULL,          # <-- Remove individual x-axis label
      y = NULL           # <-- Remove individual y-axis label
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      panel.grid.minor = element_blank()
    )
  
  # Add the plot to the list
  plot_list[[i]] <- p
}

# Combine all the plots into a grid layout
combined_plot <- wrap_plots(plot_list) + 
  plot_annotation(
    title = "Observed vs. Predicted Incidence Rates (per 1000 inhabitants)",
    theme = theme(
      plot.title = element_text(size = 12, face = "bold")
    )
  )

# Now override the axis labels once at the "global" level
combined_plot <- combined_plot & 
  labs(x = "Observed", y = "Predicted")

# Print the combined plot
print(combined_plot)

# Save the combined plot
# ggsave("obs_vs_pred.png", combined_plot, 
#        width = 10, height = 10, units = "in", dpi = 300)
```

# Plotting coeficients as networks of diseases and covariates
```{r}
library(SemiPar)
library(Hmisc)
library(qgraph)

# Load a square matrix with all diseases and covariates as rows and columns. Fill the complete matrix with values from the model coefficients, with disease-disease and covariate-covariate cells filled with zeros. 
Q <- as.matrix(read.csv("coefficients_matrix.csv", header = TRUE, row.names = 1))

# View the complete matrix
print(Q)

# excluding negative values to create the positive associations network
Q <- as.matrix(ifelse(Q>-0.2, 0, Q))

# excluding positive values to create the negative associations network
# Q <- as.matrix(ifelse(Q<0.2, 0, Q))

# Exclude rows with only zeros
Q <- Q[rowSums(Q != 0) > 0, ]

# Exclude columns with only zeros
Q <- Q[, colSums(Q != 0) > 0]


# Malaria-Chagas Negative
# {
#   node_names <- c("Rural Chagas", "Urban Chagas", "Rural malaria", "Urban malaria", "Forest degradation (2007-2017)",
#                   "Fire", "Forest edge", "Secondary vegetation", "Pasture", "Agriculture", "Urbanisation", "Roads",
#                   "Positive precipitation anomaly", "Negative precipitation anomaly","positive min. temp. anomaly",
#                   "Urban porverty", "TT class 1", "TT class 3", "TT class 4", "TT class 5",
#                   "TT class 7")
#   
#   disease <- c(rep(c("Chagas",
#                      "Malaria"),
#                    each=2),
#                rep(" Covariates",
#                    each=17))
#   } 

# Malaria-Chagas Positive

# Define node names and grouping
{ node_names <- c("Rural malaria", "Urban malaria","Rural ATL", "Urban ATL", "Rural VL", "Urban VL", 
                  "Deforestation", "Forest core", "Forest edge", "Secondary veg.",
                  "Pasture", "Agriculture", "Urbanisation", "- precip. anomaly",
                  "Urban poverty", "TT1", "TT3", "TT4",  
                  "TT5",  "TT7")
  
disease <- c(rep(c("Malaria", "ATL", "VL"),
                   each=2),
               rep("Covariates",
                   each=14))

node_labels <- c("Rural \nmalaria", "Urban \nmalaria","Rural \nATL", "Urban \nATL", "Rural \nVL", "Urban \nVL", 
                 "Deforestation", "Forest core", "Forest edge", "Secondary \nvegetation",
                 "Pasture", "Agriculture", "Urbanisation", "(-) precip. \nanomaly",
                 "Urban \npoverty", "TT1", "TT3", "TT4",  
                 "TT5",  "TT7")


node_types <- ifelse(disease %in% c("Malaria", "ATL", "VL"), "circle", "rectangle")
node_sizes <- ifelse(disease %in% c("Malaria", "ATL", "VL"), 8, 11)

# Reorder node_names and disease vectors
legend_order <- c("Rural malaria", "Urban malaria","Rural ATL", "Urban ATL", "Rural VL", "Urban VL", 
                  "Deforestation", "Forest core", "Forest edge", "Secondary veg.",
                  "Pasture", "Agriculture", "Urbanisation", "- precip. anomaly",
                  "Urban poverty", "TT1", "TT3", "TT4",  
                  "TT5",  "TT7")

node_names <- node_names[match(legend_order, node_names)]
disease <- disease[match(legend_order, node_names)]

# Node aesthetics
border_colors <- c("NA", "NA", "NA", "NA",
                   "NA", "NA", "NA", "NA",
                   "NA", "NA", "NA", "NA", 
                   "NA", "NA", "NA", "NA", 
                   "NA", "NA", "NA", "NA"
                   )

border_width <- c(0.2, 0.2, 0.2, 0.2,  
                  0.2, 0.2, 0.2, 0.2,
                  0.2, 0.8, 0.2, 0.8,
                  0.2, 0.2, 0.2, 0.2,
                  0.8, 0.2, 0.8, 0.2 
                  )

label_color <- c("black", "black", "black", "black",
                 "black", "black", "#808080", "#808080",
                 "#808080", "red4","#808080", "red4", 
                 "#808080", "#808080", "#808080", "#808080", 
                 "red4", "#808080", "red4","#808080"
)

node_color <- c("darkgreen","darkgreen", "orange","orange",
                "darkblue", "darkblue", "lightgrey", "lightgrey",
                "lightgrey", "lightgrey", "lightgrey","lightgrey",
                "lightgrey","lightgrey","lightgrey","lightgrey",
                "lightgrey","lightgrey","lightgrey","lightgrey"
)
# Create the network plot
network <- 
  qgraph(
    input = Q,
    
    #' *Important additional arguments* (p. 29)
    
    layout = 'spring', # 'circle', 'groups', 'spring'
    groups = disease, # list or vector
    minimum = 0.25, # min value to be plotted
    #maximum = 0, #max value to scale edge widths, default is absmax pcor(x,y)
    cut = 0.25, # value to initiate the scaling of edge widths
    # palette = "pastel", # 'rainbow', 'pastel', 'gray', 'R', 'ggplot2', 'colorblind'
    theme = 'Fried', # 'classic', 'gray', 'Hollywood', 'Borkulo', 'gimme',
    # 'TeamFortress', 'Reddit', 'Leuven', 'Fried', 'colorblind'
    # color = node_colors,
    color = node_color,
    edge.color = "darkgrey",
    # details = T, # if T, min/max/cut is printed under the graph
    normalize = T, # graph's normalized to look the same for all sizes
    vTrans = 125, # transparency of nodes, between 0 and 255 (no transparency)
   
    #' *Additional options for correlation/covariance matrices* (p. 30)
    
   #graph = 'glasso', # 'cor', 'pcor', 'glasso'
  # sampleSize = nrow(Q), # sample size, when graph="glasso" or minimum="sig"
    
    #' *Output arguments* (pp. 30-31)
    width = 9 * 1, # width of figure
    height = 7, # height of figure
    
    #' *Graphical arguments*
    
    # Nodes (pp. 31-32)
    
    # indicates node size, can be a vector with size for each node
    # default =  8*exp(-nNodes/80)+1
    border.width = border_width, # controls width of the border
    border.color = border_colors,  # Set the border colors for each node
    # vsize = c(5,5,5,5),
    vsize = node_sizes,
    vsize2 = 5,
    shape = node_types,
  
    # repulsion = 0.99,
    title = "(b)",
  
    # Node labels (pp. 32-33)
    # labels = names(Q), # should labels be plotted?
    labels = node_labels,  # Specify the updated node labels
    label.cex = 1, # scalar on label size
    label.color = label_color, # string on label colors
    label.prop = 1.1, # proportion of the width of the node that the label scales
    # label.norm = "OOO", # normalize width of label size in nodes
    label.scale = T, # should labels be scaled to fit the node?
    label.scale.equal = T, # should labels have same font size?
    label.fill.vertical = 0.85, # scalar indicating max prop to fill a node
    label.fill.horizontal = 0.85, # scalar indicating max prop to fill a node
    # node.label.offset = c(0.5,0.5), # where should label be centered, (x, y)
    # node.label.position = NULL, # set specific positions of node labels
    
  
    # Edges (pp. 33-34)
    negDashed = F, # should negative edges be dashed?
    trans = T, # should edges fade to white?
    fade = F, # should edges fade?
    lty = 1, # line type, see 'par'

    # Edge curvature (pp. 34-35)
    # curve = NA, # single value, a vector list, weight matrix or NA (default)
    curveAll = T, # logical indicating if all edges should be curved
    curveDefault = 0.5, # default is 1
  
     # Edge labels (p. 35)
    edge.labels = T, # if T, numeric is plotted. if F, nothing is.
    edge.label.cex = 0.9, # single number or number per edge
    edge.label.bg = T, # plot a white background behind number
    edge.label.margin = 0, # margin of the background bow around the edge label
    edge.label.position = 0.6, # vector between 0 and 1, 0.5 is middle
  
  # Layout (p. 35)
    repulsion = 0.7, # setting to lower values will cause nodes to repulse each  other less.This is useful if few unconnected nodes cause the giant
  # component to visually be clustered too much in the same place.
    
    # # Generical graphical arguments (p. 36)
    font = 1, # integer specifying default font for node and edge labels
    
    # Legend (p. 35-36)
    legend = F, # should a legend be plotted?
    legend.cex = 0.27, # scalar of the legend
    legend.mode = 'style1', # default is 'style1', different way to show legend
    GLratio = 2.5, # relative size of graph compared to the layout
    layoutScale = c(1, 1), # vector with a scalar for respectively the x and y
    # coordinates of the layout. Setting this to c(2, 2) makes plot twice as
    # big. This can be used with layoutOffset to determine the graph's placement.
    layoutOffset = c(0,0), # vector with the offset to the x and coordinates of 
    # the center of the graph
    nodeNames = node_names, # names for each node to plot in legend
    
    # Background (p. 36)
    bg = F, # should node colors cast a light in the background?
    # can also be a color...
    bgcontrol = 6, # the higher, the less light each node gives if bg = T
    bgres = 100, # (default) square root of the number of pixels used in bg = T  

    # Arguments for directed graphs (p. 36)
    directed = F, # are edges directed? can be logical vector/matrix
    arrows = T, # should arrows be plotted? can be a number
    arrowAngle = pi/8, # (default for unweighted) and pi/4 for weighted
    #' *azise* = ..., size of the arrowhead
    open = F, # should arrowheads be open?
    bidirectional = F # should directional edges between nodes have two edges?
  )
}

```
